Security Metrics for the Android Ecosystem

### 2015-07-27 security_scoring.tex
Cut some words out to make it fit on 12 pages

To allow buyers of Android devices to purchase those devices with the best security, they need to know how different device manufacturers, device models and network operators compare in terms of the security they provide.
We propose a method to score a device manufacturer, device model or network operator based on its historic performance at keeping devices up-to-date and fixing security vulnerabilities.
We find that Android as a whole gets a score of \daSecurityScore\ out of 10, the highest scoring device manufacturer is \emph{\daSecScoreBestmanufacturer} (\daSecScoreBestmanufacturerScore\ out of 10) and the lowest scoring is \emph{\daSecScoreWorstmanufacturer} (\daSecScoreWorstmanufacturerScore\ out of 10).

@@

We can compute the uncertainty for $f$, $u$ and $m$.
$f$ is computed by taking the total secure device days and dividing it by the total insecure and secure device days.
The total secure device days and total insecure device days are both counting experiments and so their measurement error is their square root~\cite{Taylor1997}.
Since the numbers involved are large, the uncertainty in $f$ is small.
$u$ is computed by taking the sum of the proportions of devices running the most recent version each day, both the count of devices running the maximum version and total count have square root uncertainties.
$m$ is computed by counting the number of vulnerabilities which affected that entity and which have not yet been fixed on any device we have observed from that entity every day and averaging over observed days.
However, it could be that the entity has released a fix to some devices but we have not yet observed a device with that fix.
So the uncertainty in our measurement is the probability of not having observed a fixed device if a fixed device existed.
We assume that if the fix has been released then at least \daMeanOutstandingProbability\ of devices have the fix.
This represents a trade-off between a proportion so small that the fix has not really been deployed and a reasonable estimate of the error.
This gives an uncertainty of \daMeanOutstandingUncertaintyEquation\ where $n$ is the number of devices contributing to that day's data for each vulnerability outstanding each day.
The Python \texttt{uncertainties} library was used to propagate uncertainties through calculations.
This does not capture systematic errors.
For example, we do not include manufacturer specific vulnerabilities, but we expect that performance in fixing manufacturer specific vulnerabilities is strongly correlated with performance fixing vulnerabilities affecting all of Android.

>>>>

To allow buyers of Android devices to purchase those devices with the best security, they need to know how different device manufacturers, device models and network operators compare in terms of security.
We propose a method to score a device manufacturer, device model or network operator based on its historic performance at keeping devices up-to-date and fixing security vulnerabilities.
We find that Android as a whole gets a score of \daSecurityScore\ out of 10, the highest scoring device manufacturer is \emph{\daSecScoreBestmanufacturer} (\daSecScoreBestmanufacturerScore) and the lowest scoring is \emph{\daSecScoreWorstmanufacturer} (\daSecScoreWorstmanufacturerScore).

@@

We can compute the uncertainty for $f$, $u$ and $m$.
$f$ is computed by taking the total secure device days and dividing it by the total insecure and secure device days.
The total secure device days and total insecure device days are both counting experiments and so their measurement error is their square root~\cite{Taylor1997}.
%Since the numbers involved are large, the uncertainty in $f$ is small.
$u$ is computed by taking the sum of the proportions of devices running the most recent version each day, both the count of devices running the maximum version and total count have square root uncertainties.
$m$ is computed by counting the number of vulnerabilities which affected that entity and which have not yet been fixed on any device we have observed from that entity every day and averaging time.
However, it could be that the entity has released a fix to some devices but we have not yet observed a device with that fix.
So the uncertainty in our measurement is the probability of not having observed a fixed device if a fixed device existed.
We assume that if the fix has been released then at least \daMeanOutstandingProbability\ of devices have the fix.
This represents a trade-off between a proportion so small that the fix has not really been deployed and a reasonable estimate of the error.
This gives an uncertainty of \daMeanOutstandingUncertaintyEquation\ where $n$ is the number of devices contributing to that day's data for each vulnerability outstanding each day.
The Python \texttt{uncertainties} library was used to propagate uncertainties through calculations.
This does not capture systematic errors.
For example, we do not include manufacturer specific vulnerabilities, we expect that performance in fixing manufacturer specific vulnerabilities is strongly correlated with performance fixing vulnerabilities affecting all of Android.

### 2015-07-27 spsm04-thomas.tex
Cut some words out to make it fit on 12 pages

%An analysis by Vidas et al.~\cite{Vidas2011} of the Android 2.1 to 2.2 update found that it took 11 months from when Google released 2.2 for the last device which they were investigating to get the update.
To compute the latency between upstream releases and the release of the first version of Android containing that release we scraped the release pages for those projects, to obtain the version numbers and release dates.
This allows us to compute the latency between an upstream project being released and it being included in Android, this is shown in Table~\ref{tab:update_ecosystem}.
The versions included in Android were about half a year old when the first version of Android containing it was released.

>>>>

%An analysis by Vidas et al.~\cite{Vidas2011} of the Android 2.1 to 2.2 update found that it took 11 months from when Google released 2.2 for the last device which they were investigating to get the update.
To compute the latency between upstream releases and the release of the first version of Android containing that release we scraped the release pages, to obtain the version numbers and release dates.
This allows us to compute the latency between an upstream project being released and it being included in Android, this is shown in Table~\ref{tab:update_ecosystem}.
The versions included in Android were about half a year old when the first version of Android containing it was released.
